---
title: "N Parameters"
author: "Sophia Yao"
format: html
execute: 
  echo: false
---

```{r}
#| label: setup
#| message: false

library(tidyverse)
library(primer.data)
library(brms)
library(tidybayes)
library(gtsummary)
```

```{r}
set.seed(9)

ch10_data <- shaming |>
  mutate(p_00 = (primary_00 == "Yes"), p_02 = (primary_02 == "Yes"),
       p_04 = (primary_04 == "Yes"), g_00 = (general_00 == "Yes"),
       g_02 = (general_02 == "Yes"), g_04 = (general_04 == "Yes"),
civ_engage = p_00 + p_02 + p_04 + g_00 + g_02 + g_04,
voter_class = case_when(civ_engage %in% c(5, 6) ~ "Always Vote",
                        civ_engage %in% c(3, 4) ~ "Sometimes Vote",
                        civ_engage %in% c(1, 2) ~ "Rarely Vote"),
voter_class = factor(voter_class, levels = c("Rarely Vote", "Sometimes Vote", "Always Vote")), age_z = as.numeric(scale(age))) |>
  rename(voted = primary_06) |>
  select(voted, treatment, sex, age_z, civ_engage, voter_class) |>
  drop_na() |>
  slice_sample(prop = 0.1)

ch10_data |>
  sample_frac(0.5) |>
  ggplot(aes(x = civ_engage, y = voted)) +
  geom_jitter(alpha = 0.03, height = 0.1) + 
  scale_x_continuous(breaks = 1:6) + 
  scale_y_continuous(breaks = c(0, 1), labels = c("No", "Yes")) + 
  labs(title = "Civic Engagement and Voting Behaviour in Michigan",
      subtitle = "Past voting predicts future voting.",
      x = "Civic Engagement",
      y = "Voted in 2006 Primary Election",
      caption = "Random sample of 5% of the data from Gerber, Green, and Larimer (2008)")
```

Using the 2006 Michigan primary elections dataset from Gerber, Green, and Larimer (2008), we aim to evaluate the causal effect of postcard mailings on voter turnout in the 2026 Texas election. The study assesses how postcard interventions impact voter behavior, noting that certain groups, like those who rarely check their mail, may be less represented in the sample of postcard recipients. Our analysis finds that age is positively related to voter turnout, with older individuals being more likely to vote. This suggests that age and other demographic factors must be considered to accurately gauge the effectiveness of postcard interventions on voter engagement.

$$
y_{i} = \beta_{0} + \beta_{1} age\_z + \beta_{2}male_i + \beta_{3}civic\_duty_i + \\ \beta_{4}hawthorne_i + \beta_{5}self_i + \beta_{6}neighbors_i + \\ \beta_{7}Sometimes\ vote_i + \beta_{8}Always\ vote_i + \\ \beta_{9}civic\_duty_i Sometimes\ vote_i + \beta_{10}hawthorne_i Sometimes\ vote_i + \\ \beta_{11}self_i Sometimes\ vote_i + \beta_{11}neighbors_i Sometimes\ vote_i + \\ \beta_{12}civic\_duty_i Always\ vote_i + \beta_{13}hawthorne_i Always\ vote_i + \\ \beta_{14}self_i Always\ vote_i + \beta_{15}neighbors_i Always\ vote_i + \epsilon_{i}
$$

```{r}
#| label: model
#| cache: true

fit_postcard_vote <- brm(formula = voted ~ age_z + sex + treatment + voter_class + treatment*voter_class, 
    data = ch10_data, 
    family = gaussian(), 
    refresh = 0, 
    silent = 2,
    seed = 19)
```

```{r}
fit_postcard_vote |>
  tbl_regression(intercept = TRUE, estimate_fun = function(x) style_sigfig(x, digits = 3))
```

```{r}
#| label: plot

ndata <- tibble()

fit_postcard_vote |>
  add_predicted_draws(newdata = ndata)
```
